Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation

### 2023-04-24 main.tex
Changes from the meeting on 24/04
Order of Authors and removed unnecessary plots

\title{Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation}
\author{Timo Betcke\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Micha\l{} Bosy\thanks{School of Computer Science and Mathematics, Kingston University London, Penrhyn Road, Kingston upon Thames, KT1 2EE, UK}, Erik Burman\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, \\ Christopher D. Cooper\thanks{Department of Mechanical Engineering and Centro Cient\'ifico Tecnol\'ogico de Valpara\'iso, Universidad T\'ecnica Federico Santa Mar\'ia, Valpara\'iso 2390123, Chile}, Matthew W. Scroggs\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}}

>>>>

\title{Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation}
\author{Micha\l{} Bosy\thanks{School of Computer Science and Mathematics, Kingston University London, Penrhyn Road, Kingston upon Thames, KT1 2EE, UK}, Matthew W. Scroggs\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Timo Betcke\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Erik Burman\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Christopher D. Cooper\thanks{Department of Mechanical Engineering and Centro Cient\'ifico Tecnol\'ogico de Valpara\'iso, Universidad T\'ecnica Federico Santa Mar\'ia, Valpara\'iso 2390123, Chile}}

### 2023-04-24 results.tex
Changes from the meeting on 24/04
Order of Authors and removed unnecessary plots

Figure \ref{fig:arg2_variable} contains the performance results of this test case, where we distinguish the iteration count from the calculation in dissolved and vacuum states. \textcolor{red}{Chris: if we don't include Fig. \ref{fig:arg2_variable}, we should remove this paragraph. I believe that if we show performance for fem-bem, a reviewer might be tempted to ask it for APBS too, which might be difficult.}  \textcolor{blue}{Michal: I completely agree. We were even talking about not putting them, but just for our information, we kept it for now. They weren't going to be in the final version}
\begin{table}
\centering
\begin{tabular}{c|c|c|c}
&Mesh size  & Grid points & $\Delta G_{solv}$\\
&\AA       & &  kcal/mol \\
\hline
\multirow{4}{*}{APBS}& 0.52$\times$0.52$\times$0.52 & 97$\times$97$\times$97 & -107.6186 \\ 
& 0.39$\times$0.39$\times$0.39 & 129$\times$129$\times$129 & -107.8752\\ 
&0.26$\times$0.26$\times$0.26 & 193$\times$193$\times$193& -108.3378\\ 
&0.195$\times$0.195$\times$0.195 & 257$\times$257$\times$257& -108.5837\\ 
&0.098$\times$0.098$\times$0.098 & 513$\times$513$\times$513& -108.8844\\ 
\hline
&Mesh dens. & DOFs & $\Delta G_{solv}$\\
&vert/\AA$^2$   &  &  kcal/mol \\
\hline
%\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
    & 4.1 & 3 491 & -109.933 \\
FEM-BEM    & 6.7  & 5 787 & -110.238 \\
coupling    & 8.57  & 8 844 & -109.658 \\
    & 17 & 19 911 & -109.368 \\
    & 24.5 & 32 302 & -109.286 \\
\hline
%\multirow{5}{*}{Standard FEM-BEM}& 2 & -29.554\\
%    & 2 & -34.670\\
%Hybrid    & 4  & -33.603 \\
%FEM-BEM    & 8  & -32.822 \\
%    & 16 & -32.072 \\
%\hline
\end{tabular}
\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the FEM-BEM approach and APBS. The mesh density for FEM-BEM corresponds to the vertex density of the surface mesh used to generate the volumetric mesh.}
\label{table:arg_variable}
\end{table}

%\begin{figure}
%\centering
%% \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter.png}
%% \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time.png}
%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time_11.png}
%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_setup_time_11.png}
%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter_11.png}
%\caption{Iteration count and time-to-solution to compute the solvation energy of arginine with a variable permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems), using FEM-BEM coupling. %Can we make this only two plots?
%}
%\label{fig:arg_variable}
%\end{figure}

\begin{figure}
\centering
% \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_iter.png}
% \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_time.png}
\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_time.png}
\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_set_time.png}
\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_iter.png}
\caption{Iteration count and time-to-solution to compute the solvation energy of arginine with a variable permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems), using FEM-BEM coupling. %Can we make this only two plots?
\textcolor{red}{Chris: not sure if we want to show performance here. Reviewers may ask for performance with APBS too, and those were run on a different machine, and has a number of steps.}}
\label{fig:arg2_variable}
\end{figure}

@@

\begin{table}
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{c|c|c|c|c|c|c|c|c}
Molecule & FEM  & BEM &  $\Delta G_{solv}$ & Iterations & Setup Time & Solving Time & Solv. time per & Total Time \\
& DOFs & DOFs &  kcal/mol & & [sec] & [sec] & iter. [sec] & [sec] \\
\hline
 1pgb  & 29 434 &  10 058 &  -300.888 & 826 & 82 & 547 & 0.6 & 6 629  \\
 1lyz  & 56 114 & 18 606 &  -599.642 & 1 285 & 330 & 1 640  & 1.2 & 1 970  \\
 %1lyz gs3 & 257 391 & 75 048 &  -600.637 & 2 949  & 1 690 & 10 900 & 3.6 & 12 590   \\
 1x1u & 263 181 & 81 258 \textcolor{red}{82360} \textcolor{blue}{???}&  -1 984.468 & 4 167 & 8 240 & 16 300 & 3.91 & 24 540  \\
 1igt & 597 575 & 187 712 \textcolor{red}{189960}  \textcolor{blue}{???}&   -3 294.230 & 8 361 & 41 200 & 64 200 & 7.67  &  105 400   \\
 \hline
\end{tabular}}
\caption{Results for larger structures with a variable permitivitty.}
\label{table:large_variable}
\end{table}
%
%\begin{table}
%\centering
%\begin{tabular}{c|c|c|c|c|c|c|c|c}
%Molecule & Mesh size  & FEM  & BEM &  $\Delta G_{solv}$ & Iterations & Setup Time & Solving Time & Total Time \\
%& vert/\AA$^2$ & DOFs & DOFs &  kcal/mol & & sec & sec & sec \\
%\hline
% 1pgb &  & 29 434 &  10 058 &  -300.888 & 826 & 82 & 547 & 629  \\
% 1lyz &  & 56 114 & 18 606 &  -599.642 & 1 285 & 330 & 1 640  & 1 970  \\
% 1lyz gs3 &  & 257 391 & 75 048 &  -600.637 & 2 949  & 1 690 & 10 900 & 12 590   \\
% 1uxu &  & 263 181 & 81 258 &  -1 984.468 & 4 167 & 8 240 & 16 300 & 24 540  \\
% 1igt &  & 597 575 & 187 712 &   -3 294.230 & 8 361 & 41 200 & 64 200 &  105 400   \\
% \hline
%\end{tabular}
%\caption{Large tests' results}
%\label{table:large_variable}
%\end{table}

>>>>

%Figure \ref{fig:arg2_variable} contains the performance results of this test case, where we distinguish the iteration count from the calculation in dissolved and vacuum states. \textcolor{red}{Chris: if we don't include Fig. \ref{fig:arg2_variable}, we should remove this paragraph. I believe that if we show performance for fem-bem, a reviewer might be tempted to ask it for APBS too, which might be difficult.}  \textcolor{blue}{Michal: I completely agree. We were even talking about not putting them, but just for our information, we kept it for now. They weren't going to be in the final version}
\begin{table}
\centering
\begin{tabular}{c|c|c|c}
&Mesh size  & Grid points & $\Delta G_{solv}$\\
&\AA       & &  kcal/mol \\
\hline
\multirow{4}{*}{APBS}& 0.52$\times$0.52$\times$0.52 & 97$\times$97$\times$97 & -107.6186 \\ 
& 0.39$\times$0.39$\times$0.39 & 129$\times$129$\times$129 & -107.8752\\ 
&0.26$\times$0.26$\times$0.26 & 193$\times$193$\times$193& -108.3378\\ 
&0.195$\times$0.195$\times$0.195 & 257$\times$257$\times$257& -108.5837\\ 
&0.098$\times$0.098$\times$0.098 & 513$\times$513$\times$513& -108.8844\\ 
\hline
&Mesh dens. & DOFs & $\Delta G_{solv}$\\
&vert/\AA$^2$   &  &  kcal/mol \\
\hline
%\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
    & 4.1 & 3 491 & -109.933 \\
FEM-BEM    & 6.7  & 5 787 & -110.238 \\
coupling    & 8.57  & 8 844 & -109.658 \\
    & 17 & 19 911 & -109.368 \\
    & 24.5 & 32 302 & -109.286 \\
\hline
%\multirow{5}{*}{Standard FEM-BEM}& 2 & -29.554\\
%    & 2 & -34.670\\
%Hybrid    & 4  & -33.603 \\
%FEM-BEM    & 8  & -32.822 \\
%    & 16 & -32.072 \\
%\hline
\end{tabular}
\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the FEM-BEM approach and APBS. The mesh density for FEM-BEM corresponds to the vertex density of the surface mesh used to generate the volumetric mesh.}
\label{table:arg_variable}
\end{table}

%%\begin{figure}
%%\centering
%%% \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter.png}
%%% \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time.png}
%%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time_11.png}
%%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_setup_time_11.png}
%%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter_11.png}
%%\caption{Iteration count and time-to-solution to compute the solvation energy of arginine with a variable permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems), using FEM-BEM coupling. %Can we make this only two plots?
%%}
%%\label{fig:arg_variable}
%%\end{figure}
%
%\begin{figure}
%\centering
%% \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_iter.png}
%% \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_time.png}
%\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_time.png}
%\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_set_time.png}
%\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_iter.png}
%\caption{Iteration count and time-to-solution to compute the solvation energy of arginine with a variable permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems), using FEM-BEM coupling. %Can we make this only two plots?
%\textcolor{red}{Chris: not sure if we want to show performance here. Reviewers may ask for performance with APBS too, and those were run on a different machine, and has a number of steps.}}
%\label{fig:arg2_variable}
%\end{figure}

@@

\begin{table}
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{c|c|c|c|c|c|c|c|c}
Molecule & FEM  & BEM &  $\Delta G_{solv}$ & Iterations & Setup Time & Solving Time & Solv. time per & Total Time \\
& DOFs & DOFs &  kcal/mol & & [sec] & [sec] & iter. [sec] & [sec] \\
\hline
 1pgb  & 29 434 &  10 058 &  -300.888 & 826 & 82 & 547 & 0.6 & 6 629  \\
 1lyz  & 56 114 & 18 606 &  -599.642 & 1 285 & 330 & 1 640  & 1.2 & 1 970  \\
 %1lyz gs3 & 257 391 & 75 048 &  -600.637 & 2 949  & 1 690 & 10 900 & 3.6 & 12 590   \\
 1x1u & 263 181 & 81 258 &  -1 984.468 & 4 167 & 8 240 & 16 300 & 3.91 & 24 540  \\
 1igt & 597 575 & 187 712 &   -3 294.230 & 8 361 & 41 200 & 64 200 & 7.67  &  105 400   \\
 \hline
\end{tabular}}
\caption{Results for larger structures with a variable permitivitty.}
\label{table:large_variable}
\end{table}
%
%\begin{table}
%\centering
%\begin{tabular}{c|c|c|c|c|c|c|c|c}
%Molecule & Mesh size  & FEM  & BEM &  $\Delta G_{solv}$ & Iterations & Setup Time & Solving Time & Total Time \\
%& vert/\AA$^2$ & DOFs & DOFs &  kcal/mol & & sec & sec & sec \\
%\hline
% 1pgb &  & 29 434 &  10 058 &  -300.888 & 826 & 82 & 547 & 629  \\
% 1lyz &  & 56 114 & 18 606 &  -599.642 & 1 285 & 330 & 1 640  & 1 970  \\
% 1lyz gs3 &  & 257 391 & 75 048 &  -600.637 & 2 949  & 1 690 & 10 900 & 12 590   \\
% 1uxu &  & 263 181 & 81 258 &  -1 984.468 & 4 167 & 8 240 & 16 300 & 24 540  \\
% 1igt &  & 597 575 & 187 712 &   -3 294.230 & 8 361 & 41 200 & 64 200 &  105 400   \\
% \hline
%\end{tabular}
%\caption{Large tests' results}
%\label{table:large_variable}
%\end{table}
